FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-08-16 paper.tex
Finish §3.2 edits

\FT{} can produce copious amounts of log files which can be challenging to sift through manually.
Coalesced Stack Trace Graphs, or CSTGs\cite{humphreySystematicDebuggingMethods2014} provide a way to visualize large amounts of stack traces in a compact form.
CSTG is a stand-alone tool and was not designed with \FT{} specifically in mind.
However, it pairs well with \FT{} and makes coming through the log files easier.

@@

CSTG's output looks like the output seen in \cref{fig:sw_nan_cstg}, which was generated by running \FT{} on a library called ShallowWaters.
We will go into more detail about ShallowWaters in \cref{s:sw}.
This graph has been edited for clarity and to fit into the size constraints of this paper.

@@

% Acknowledge that apps get offloaded to GPU; FT doesn't do that, but there's this companion tool…
% You run it on a kernel; catches things not caught by GPUs; see Oceananigans as an example below
% TODO: add note in future work/discussion about this as well; other languages too—not just GPU
% FloatTracker could supply an API that wraps calls to a C library—lib is still a black box, but FT gives you a big picture

@@

\begin{figure}
  \centering
  \includegraphics[width=3in]{./fig/float_tracker_context_boxes.png}
  \caption{FloatTracker and GPU-FPX compliment each other}
  \label{fig:ft_and_gpu_fpx}
\end{figure}

>>>>

\FT{} can produce copious amounts of log files which can be challenging to sift through manually.
Coalesced Stack Trace Graphs, or CSTGs~\cite{humphreySystematicDebuggingMethods2014} provide a way to visualize large amounts of stack traces in a compact form.
CSTG is a stand-alone tool and was not designed with \FT{} specifically in mind.
However, it pairs well with \FT{} and makes analyzing the log files easier.

@@

@@

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=3in]{./fig/float_tracker_context_boxes.png}
  \caption{FloatTracker and GPU-FPX compliment each other}
  \label{fig:ft_and_gpu_fpx}
\end{figure}
